Verifying Demonstrations

### 2018-05-25 paper/RelatedWork.tex
Edits the related works section

The seemingly most commonly used method for counting crowds at protests is 
\emph{Jacobs's method}, \cf~\cite{%
  2016DemonstrationsInSeoul,%
  BBCHowToCountProtestNumbers,%
  HowWillWeKnowTrumpInauguralCrowdSize,%
  TheXManMarch,%
  TheCrowdNumbersGame,%
}.
It is a manual method devised in the 1960s relying on aerial photos of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions and finally sums them up to get an estimate of the global count.
Clearly this method is prone to errors as it is based on estimates.
It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same photos.
However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial photos.}.
We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
However, this is prone to cheating and the best we can do is to employ forensic methods to try to detect any modifications or other attempts at fraud.
\seb{maybe we should also give information about the privacy level reached by 
  this different method}

Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd 
based on a selected space.
Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
\seb{what are the meaning of the choice of density estimates, it is a way to 
  specify an apriori assumption about the density of the crowd or to choose 
  between a min, average, max estimates?}
This is similar to the method usually used by police (\eg for the protests in Seoul):
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{p}olice presume\textins*{d} that, when sitting, six people would 
  fill a space of 
  3.3 square meters
  \textelp{}
  The same area would hold nine or 10 people when standing%
}.
This method is not verifiable unless the user takes a picture of the crowd, in which case it inherits the verifiability properties of the previous method.

@@

\daniel{I think we can cut this paragraph as it is not directly relevant}
\Citet{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the Wi-Fi signal as a sonar to detect people.
However this method is designed for indoor use and does not scale to more than a 
crowd of 20 persons, which makes it unfit to use in protest.
In addition, this type of data does not provide verifiability.

>>>>

The seemingly most commonly used method for counting crowds at protests is 
\emph{Jacobs's method}, \cf~\cite{%
  2016DemonstrationsInSeoul,%
  BBCHowToCountProtestNumbers,%
  HowWillWeKnowTrumpInauguralCrowdSize,%
  TheXManMarch,%
  TheCrowdNumbersGame,%
}.
It is a manual method devised in the 1960s relying on aerial photos of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions and finally sums them up to get an estimate of the global count.
Clearly this method is prone to errors as it is based on estimates.
It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same photos.
However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial photos.}.
We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
However, this is prone to cheating --- and subject to a variety of 
misinformation techniques --- and the best we can do is to employ forensic 
methods to try to detect any modifications or other attempts at fraud.

\seb{maybe we should also give information about the privacy level reached by 
  this different method}
From a privacy perspective, all techniques based on photo or video material are 
as privacy preserving as the protesters make themselves.
There is a risk that participants are recognizable from the material if they do 
not wear masks.

Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd 
based on a selected space.
Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
\seb{what are the meaning of the choice of density estimates, it is a way to 
  specify an apriori assumption about the density of the crowd or to choose 
  between a min, average, max estimates?}
\daniel{Yes.}
This is similar to the method usually used by police (\eg for the protests in Seoul):
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{p}olice presume\textins*{d} that, when sitting, six people would 
  fill a space of 
  3.3 square meters
  \textelp{}
  The same area would hold nine or 10 people when standing%
}.
This method is not verifiable unless the user takes a picture of the crowd, in which case it inherits the verifiability properties of the previous method.

@@
